ASYMPTOTIC VALIDITY OF THE BAYES-INSPIRED INDIFFERENCE ZONE PROCEDURE:

### 2015-07-02 paper/wish/wsc15paper.tex
good selectiongood selection

This paper considers the indifference-zone (IZ) formulation of the ranking and selection problem, in which we require that a procedure satisfy the IZ guarantee, i.e., that the best system be chosen with probability larger than some threshold $P^*$ given by the user, when the distance between the best system and the others is larger than some other user-specified threshold $\delta>0$.  The set of problem configurations satisfying this constraint on the difference in means is called the preference zone.
The paper \citeN{Bechhofer:1954} is considered the seminal work, and early work is 
presented in the monograph \citeN{Bechhofer:1968}. Some compilations of the theory developed in the area can be found
in \citeN{Bechhofer:1995}, \citeN{swisher:survey}, \citeN{kim:20062} and \citeN{kim:2007}. Other approaches, beyond the indifference-zone approach, include the Bayesian approach \cite{Frazier:Tutorial}, the optimal computing budget allocation approach \cite{chen:ocva}, and the large deviations approach \cite{glynn2004large}.

@@

\citeN{Frazier:BIZ} presents a new sequential elimination
IZ procedure, called BIZ (Bayes-inspired Indifference Zone), 
that eliminates the use of Bonferroni's inequality, reducing conservatism. 
This procedure's lower bound on the worst-case probability of correct selection in the
preference zone is tight in continuous time, and almost tight in discrete time. In numerical experiments, the number of samples required
by BIZ is significantly smaller than that of procedures like the $\mathcal{P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968} and the KN procedure of \citeN{Kim:2001}, especially on problems with many alternatives. Unfortunately, the
proof from \citeN{Frazier:BIZ} that the BIZ procedure satisfies the IZ guarantee for the discrete-time case assumes that (1) samples are normally distributed; 
(2) variances are known;
and (3) the variances are either common across alternatives, or have an unrealistic integer multiple structure.

>>>>

This paper considers the indifference-zone (IZ) formulation of the ranking and selection problem, in which we require that a procedure satisfy the IZ guarantee, i.e., that the best system be chosen with probability larger than some threshold $P^*$ given by the user, when the distance between the best system and the others is larger than some other user-specified threshold $\delta>0$.  The set of problem configurations satisfying this constraint on the difference in means is called the preference zone.
The paper \citeN{Bechhofer:1954} is considered the seminal work, and early work is 
presented in the monograph \citeN{Bechhofer:1968}. Some compilations of the theory developed in the area can be found
in \citeN{Bechhofer:1995}, \citeN{swisher:survey}, \citeN{kim:20062} and \citeN{kim:2007}. Other approaches, beyond the indifference-zone approach, include the Bayesian approach \cite{Frazier:Tutorial}, the optimal computing budget allocation approach \cite{chen:ocva}, the large deviations approach \cite{glynn2004large}, and the probability of good selection guarantee \cite{nelson2001selecting}. The last approach is similar to the indifference-zone formulation, but provides a more robust guarantee.

@@

\citeN{Frazier:BIZ} presents a new sequential elimination
IZ procedure, called BIZ (Bayes-inspired Indifference Zone), 
that eliminates the use of Bonferroni's inequality, reducing conservatism. \mathcal
This procedure's lower bound on the worst-case probability of correct selection in the
preference zone is tight in continuous time, and almost tight in discrete time. In numerical experiments, the number of samples required
by BIZ is significantly smaller than that of procedures like the ${P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968} and the KN procedure of \citeN{Kim:2001}, especially on problems with many alternatives. Unfortunately, the
proof from \citeN{Frazier:BIZ} that the BIZ procedure satisfies the IZ guarantee for the discrete-time case assumes that (1) samples are normally distributed; 
(2) variances are known;
and (3) the variances are either common across alternatives, or have an unrealistic integer multiple structure.
